---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```



<!--

https://github.com/maierhofert/classiFunc


# fda.usc
README.md is generated from README.Rmd. Please edit that file 
#[![Travis-CI Build Status](https://api.travis-ci.org/maierhofert/classiFunc.svg?branch=master)](https://travis-ci.org/maierhofert/classiFunc)
#[![packageversion](https://img.shields.io/badge/Package%20version-0.1.1-orange.svg?style=flat-square)](https://CRAN.R-project.org/package=classiFunc)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/fda.usc)](https://cran.r-project.org/package=fda.usc)
[![](https://cranlogs.r-pkg.org/badges/fda.usc)](https://cran.r-project.org/package=fda.usc)
# [![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)

Incluir reference card
-->



## Package overview

**fda.tsc** Functional Data Sets of  UEA & UCR Time Series Classification Repository [Time Series Classification Repository](http://www.timeseriesclassification.comadapted for using in package  **fda.usc**.  The **fda.usc** package implements methods  for exploratory and descriptive analysis of functional data such as depth measurements, atypical curves detection, regression models, supervised classification, unsupervised classification and functional analysis of variance.


## Installation

You can install the latest patched version from Github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
library(devtools)
devtools::install_github("moviedo5/fda.tsc")
```


This package contains a datasets availabe in 
[Time Series Classification Web Page](http://timeseriesclassification.com/dataset.php) converted in `fdata` class objects (of  \code{fda.usc} packages.   The vignette gives a quick introduction to the usage of the `fda.tsc` package.


## Dependencies
The fda.tsc package depends on the fda.usc R-packages. For installation instructions, see below.

A hands on introduction to \code{fda.usc} package can be found in the reference [vignette](https://www.jstatsoft.org/index.php/jss/article/view/v051i04/v51i04.pdf).

Details on specific functions are in the [reference manual](https://cran.r-project.org/package=fda.usc/fda.usc.pdf), Manuel Oviedo PhD thesis [Advances in functional regression and classification models](http://hdl.handle.net/10347/18236)


List of TSC datasets:  

```{r, eval = TRUE,message=FALSE,warning=FALSE}
library("fda.tsc")
# data(package = "fda.tsc") # Shows the package dataset
d <- data(package = "fda.tsc")
## names of data sets in the package
#d$results[, "Item"]
nm <- d$results[, "Item"]
## assign it to use later 
data(list = nm, package = "fda.tsc")
# lfdata: list with the datasets
list.fdata <- mget(nm) 
#names(list.fdata)
```

```{r, eval = TRUE,message=FALSE,warning=FALSE}
aa<-d$results[, "Package"]
#length(aa);class(aa)
ivar <-  c("Package","Item")
tabla<-data.frame(d$results[,ivar])
names(tabla)<-ivar
tabla$ncurves <-as.numeric(unlist(lapply(seq_along(list.fdata), function(i) nrow(list.fdata[[i]]$x))))
tabla$n_argvals <- as.numeric(unlist(lapply(seq_along(list.fdata), function(i) ncol(list.fdata[[i]]$x))))
#names(tabla)
tab1 <-unlist(lapply(seq_along(list.fdata), function(i)   nlevels(list.fdata[[i]]$df[,"class"])))
tab2 <-matrix(unlist(lapply(seq_along(list.fdata), function(i)   table(list.fdata[[i]]$df[,"sample"]))),ncol=2,byrow=T)
tabla<-cbind(tabla,tab1,tab2[,2:1])
names(tabla)[5:7]<-c("nlevels","n_train","n_test")
#head(tabla)
#mapply(function(x, i) paste(i, x), x, names(x))
## call the promised data
#data(list = nm, package = "fda.tsc")
## get the dimensions of each data set
# lapply(mget(nm), dim)
 #lapply(mget(nm)[[1]], class)
#install.packages("vcdExtra")
#vcdExtra::datasets("fda.tsc")
```


A ver peta

```{r, eval = TRUE,message=FALSE,warning=FALSE, echo=FALSE}
library(knitr)
kable(tabla,caption="Table: Time Series Classification Datasets adapted for fda.usc package")

```




