---
title: "fda.tsc: Functional Data Sets for Time Series Classification"
author: "Manuel Oviedo de la Fuente"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fda.tsc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
This vignette gives a quick introduction to the key features included in the `fda.usc` package. Please use the [Project Page](https://github.com/moviedo5/fda.tsc/) to suggest new features or report bugs. This package contains a datasets availabe in 
[Time Series Classification Web Page](http://timeseriesclassification.com/dataset.php) converted in `fdata` class objects (of  \code{fda.usc} packages.   The following chunk gives a quick introduction to the usage of the `fda.tsc` package.
 
List of TSC datasets:  

```{r, eval = TRUE,message=FALSE,warning=FALSE}
library("fda.tsc")
# data(package = "fda.tsc") # Shows the package dataset
d <- data(package = "fda.tsc")
## names of data sets in the package
#d$results[, "Item"]
nm <- d$results[, "Item"]
## assign it to use later 
data(list = nm, package = "fda.tsc")
# lfdata: list with the datasets
list.fdata <- mget(nm) 
#names(list.fdata)
```

```{r, eval = TRUE,message=FALSE,warning=FALSE}
aa<-d$results[, "Package"]
#length(aa);class(aa)
ivar <-  c("Package","Item")
tabla<-data.frame(d$results[,ivar])
names(tabla)<-ivar
tabla$ncurves <-as.numeric(unlist(lapply(seq_along(list.fdata), function(i) nrow(list.fdata[[i]]$x))))
tabla$n_argvals <- as.numeric(unlist(lapply(seq_along(list.fdata), function(i) ncol(list.fdata[[i]]$x))))
#names(tabla)
tab1 <-unlist(lapply(seq_along(list.fdata), function(i)   nlevels(list.fdata[[i]]$df[,"class"])))
tab2 <-matrix(unlist(lapply(seq_along(list.fdata), function(i)   table(list.fdata[[i]]$df[,"sample"]))),ncol=2,byrow=T)
tabla<-cbind(tabla,tab1,tab2[,2:1])
names(tabla)[5:7]<-c("nlevels","n_train","n_test")
#head(tabla)
#mapply(function(x, i) paste(i, x), x, names(x))
## call the promised data
#data(list = nm, package = "fda.tsc")
## get the dimensions of each data set
# lapply(mget(nm), dim)
 #lapply(mget(nm)[[1]], class)
#install.packages("vcdExtra")
#vcdExtra::datasets("fda.tsc")
```

```{r, eval = TRUE,message=FALSE,warning=FALSE, echo=FALSE}
#library(knitr)
#kable(tabla,caption="o e oe eo")
#data.table::data.table(tabla)

#install.packages("DT")
library(DT)
datatable(tabla)
#editable = TRUE)
#DT:::DT2BSClass('display')
## [1] "table table-striped table-hover"
#DT:::DT2BSClass(c('compact', 'cell-border'))
## [1] "table table-condensed table-bordered"
#datatable(head(mtcars), rownames = head(LETTERS))  # new row names
#colnames = c('Here', 'Are', 'Some', 'New', 'Names')
#datatable(  head(iris),
#  caption = htmltools::tags$caption(
 #   style = 'caption-side: bottom; text-align: center;',
  #  'Table 2: ', htmltools::em('This is a simple caption for the table.')  ))

```


# Functional data classification example

## `fda.tsc` read the data sets and shows a brief description


Example of classification using non-parametric (kNN and kernel) classifier using ArrowHead dataset:


```{r, eval = TRUE, message=FALSE,warning=FALSE,echo=FALSE}
subset.lfdata<-function(x,subset,select,drop=TRUE,...){
  #if (any(class(x)!="lfdata")) stop("No list class object")
  # ver si es neceario, igual ahora ya se carga con fda.usc
  nvar<-length(x)
  namx=names(x)
  newx<-x
  for (i in 1:nvar){
	if (is.fdata(x[[i]])) {
    newx[[i]]<-subset.fdata(x[[i]],subset,select,drop,...)
		} else {
	newx[[i]]<-subset(x[[i]],subset,select,drop,...)	
		}
  } 
  return(invisible(newx))
}
```


  
Pruebas de GLM vs GLM-KFOLD

```{r, eval = TRUE, message=FALSE,warning=FALSE,cache=TRUE}
   
name_classif <- c("glm.pc","glm.bsp")
ind.classif <- c(1,3,6,7,8,9,10,12,16,17,18,19,20,23,26,28,30,32,33,34,36,
                   40,43,46,58,59,60,63,64,65,70,72)
ind.classif <- c(1,3,6,7,8,9,10,20,23,26,28,30,32,33,34,36,
                   40,43,46,58,59,60,63,64,65,70,72)
ndigits <- 2
name_dataset <- names(list.fdata)[ind.classif]
n_datasets <- length(name_dataset)
n_classif <- length(name_classif)
error.train <- error.test<- array(NA,dim=c(n_datasets,n_classif))
par.classif <- list()
formula<- formula(class~x)
  for (i in 1:n_datasets){ 
     laux <- list.fdata[[ind.classif[i]]]
     data.train <- subset.lfdata(laux,subset= laux$df$sample=="train")
     data.test  <- subset.lfdata(laux,subset= laux$df$sample=="test")
     lev <- levels(laux$df$class)
     levels(data.train$df$class)<-lev
     levels(data.test$df$class)<-lev
    # kNN classifiers with L2 distance (default) of the curves
    #res1 = classif.knn(group = data.train$df$class, fdataobj = data.train$x, knn =1)
    # Kernel classifiers with L2 distance (default) of the curves
    #res2 = classif.kernel(group = data.train$df$class, fdataobj = data.train$x)
     lpc <- list("x"=create.pc.basis(data.train$x,1:3))
     res.pc = classif.glm(class ~x, data = data.train,basis.x=lpc)
     
     lbsp <- list("x"=create.fdata.basis(data.train$x,1:15,type.basis="bspline"))
     res.bsp = classif.glm(class ~x, data = data.train,basis.b=lbsp)
     pred1 = predict(res.pc,  data.test)
     pred2 = predict(res.bsp, data.test)
     error.test[i,]<-c(mean(pred1 != data.test$df$class),  
                      mean(pred2 != data.test$df$class))
      error.test[i,]
    #save(kk,file="kk.RData")
  }
  dimnames(error.test)<-list(name_dataset,paste0("error_",name_classif,".test"))
  tabla.mis<-data.frame(tabla[ind.classif,],
                        round(error.test,ndigits))
```

```{r, eval = TRUE,message=FALSE,warning=FALSE, echo=FALSE}
print(colnames(tabla.mis))
#datatable(tabla.mis[,c(5,4,6,8,7,9)],rownames = name_dataset )
#datatable(tabla.mis[,c(5,4,6,7,8,10,11,9,12,13)],rownames = name_dataset)
datatable(tabla.mis[,-c(1,2)],rownames = name_dataset)
```
  